---
title: "Midterm 2"
author: "Sum 1"
date: "18/03/2021"
output:
  word_document: default
  pdf_document: default
---
1st likelihood ratio Test H_0: transformation parameter is equal to 0 vs H_1: transformation parameter is not equal to 0.
  2nd likelihood Ratio test H_0: no transformation is needed vs H_1: Transformation is needed
Both tests got rejected at 0.05 level of significance, so we conclude that a transformation is required which is not logarithmic.
Based on the output given in question the transformation should be Y^(-0.4471). Also the box-cox plot indicates the peek at somewhere near -0.5.


```{r}
library("alr4")
library("MASS")
attach(BigMac2003)
m1=lm(BigMac~.,data=BigMac2003)
```
```{r}
powerTransform(m1)
summary(powerTransform(m1))
```
Yes,we need to transform the variable since both p values are <0.05
Required Transformation Y^-(0.3117)
```{r}
m2=lm(BigMac^(-0.3117)~.,data=BigMac2003)
m3=lm(BigMac^(-0.3117)~1)
stepAIC(m3,k=log(length(BigMac)),direction="forward",scope = formula(m2))
```
No all variables are not needed in the model base on forward stepwise selection using BIC.Regression with required variables are as follows
```{r}
m4=lm(BigMac^(-0.3117)~TeachGI + Rice + FoodIndex + Bread)
summary(m4)
SR=studres(m4)
```
Yes,there are potential outliers. They are as follows\
```{r}
which(abs(SR)>2)
```
Note:I have used critical value of t_0.05 as 2 instead of 1.96(Z_0.05)
```{r}
CD=cooks.distance(m4)
which(CD>3)
```
There are no influential observations.


```







